A Formal Logic for Formal Category Theory

### 2022-10-14 paper/paper.tex
short Adjoint example

>>>>

\begin{lemma}[Equivalent Definitions of Adjoints]
  We show that given a morphism of profunctors
  \[ \homunary \alpha {\punitinXfromYtoZ{} {L\alpha} \beta} \beta {\punitinXfromYtoZ {} \alpha {R \beta}}\]
  we can extract a unit natural transformation $\eta : \pendallXdotY
  \alpha \punitinXfromYtoZ {}{\alpha}{R(L\alpha)}$ and vice-versa.
\end{lemma}
\begin{proof}
  The construction is exactly the ordinary proof but formalized in \vett{} syntax.
  Given the morphism of profunctors $M$, we define the unit by evaluating at the identity:
  \[ \pendallXdotY \alpha \appunary M \alpha {\punitrefl \alpha} \alpha \]
  and given the unit $\eta$, we can define a morphism of profunctors
  by composing the unit with the functorial lift of the input:
  \[ \homunary \alpha {f} \beta \textrm{comp}(\pendappXtoY \eta \alpha, \textrm{fctor}(R)(f))\]
  That this is an isomorphism follows by a similar argument to the
  proof of the Yoneda lemma.
\end{proof}
